Lipids and dementia\\ An investigation of their relationship

### 2020-02-07 _00-introduction.Rmd
Add word count

# Introduction {-}

@@

Welcome to my thesis!

>>>>

# Covering material {-}

@@

```{r word-count, echo=FALSE, warning=FALSE}
words <-
  wordcountaddin::word_count("01-Chp1-Introduction.Rmd") +
  wordcountaddin::word_count("02-Chp2-Systematic-Review.Rmd")

date <- as.character(format(Sys.time(),"%d%m%Y"))

tmpWords <- data.frame(words = words, date = date)

masterWords <- read.csv("words/words.csv", header = TRUE)

masterWords <- rbind(masterWords,tmpWords)

write.csv(file = "words/words.csv", x = masterWords, col.names = FALSE, row.names = FALSE)
```

Word count: `r words`

### 2020-02-07 docs/5abd0cd3e96bf9459398f146495c15129ee56682/_main.tex
Add word count

% all your chapters and appendices will appear here
\hypertarget{introduction}{%
\chapter*{Introduction}\label{introduction}}
\addcontentsline{toc}{chapter}{Introduction}

@@

Welcome to my thesis!

@@

The following tools were used to perform risk of bias assessments: ROB-2, ROBINS-I and QUADAS-2

>>>>

% all your chapters and appendices will appear here
\hypertarget{covering-material}{%
\chapter*{Covering material}\label{covering-material}}
\addcontentsline{toc}{chapter}{Covering material}

@@

\begin{verbatim}
## For information on available language packages for 'koRpus', run
## 
##   available.koRpus.lang()
## 
## and see ?install.koRpus.lang()
\end{verbatim}

Word count: 1163

@@

The following tools were used to perform the risk of bias assessments: ROB-2, ROBINS-I and QUADAS-2
